Algorithmic Approaches to Match Degraded Land Impressions

### 2017-10-20 degraded-paper.Rmd
Acknowledgment
all but fig 13

p1 <- ggplot(data = final_profs, aes(x = y, y = l30, colour = profile_id)) +
    geom_line() +
    theme_bw()

p2 <- ggplot(data = final_doublesmoothed, aes(x = y, y = l30, colour = profile_id)) +
    geom_line() +
    geom_smooth(inherit.aes = FALSE, aes(x = y, y = avgl30), colour = "purple") +
    theme_bw()

p3 <- ggplot(data = final_doublesmoothed, aes(x = y, y = l50, colour = profile_id)) +
    geom_line() +
    theme_bw()

@@

```{r roughcordist, echo=FALSE, fig.cap='Empirical CDFs of the Roughness Correlation compared to the CCF for known matches and known non-matches. It can be seen that the distribution of each feature for the known non-matches is quite symmetric, while the distribution for each feature for the known matches is skewed left.'}
cor_compare <- CCFs_withlands %>%
  select(ccf, rough_cor, match) %>%
  gather(key = feature, value = value, ccf, rough_cor) %>%
  mutate(match = factor(match, labels = c("Known non-matches (KNM)", "Known matches (KM)")))

ggplot(data = cor_compare, aes(x = value, color = match)) +
  stat_ecdf() +
  facet_wrap(~feature, nrow = 2) +
  theme_bw() + ylab("") + xlab("") +
  scale_color_brewer("Bullet Land Pairs", palette="Paired") +
  theme(legend.background = element_rect(colour="grey75"),
        axis.title.y=element_blank(),
        plot.margin = unit(c(0,0,0,0), unit="cm"))
```

@@

CCFs_test_normalized <- CCFs_test %>% select(Type, ccf, rough_cor, D, matches, mismatches, cms, non_cms, sum_peaks)
CCFs_test_normalized[,-1] <- lapply(CCFs_test_normalized[,-1], function(x) { (x - mean(x, na.rm = TRUE)) / sd(x, na.rm = TRUE) })
pcp_data <- CCFs_test_normalized %>%
  group_by(Type) %>%
  summarise_each(funs(mean))
pcp_data_tall <- pcp_data %>%
  gather(key = Feature, value = Value, 2:ncol(.))
CCFs_tall <- CCFs_test_normalized %>%
  mutate(id = 1:nrow(.)) %>%
  select(id, everything()) %>%
  gather(key = Feature, value = Value, 3:ncol(.))

p1 <- ggplot() +
  geom_line(data = filter(CCFs_tall, Type %in% c("True Positive")), aes(x = Feature, y = Value, colour = Type, group = id), alpha = 0.1, size = 0.2, linetype = "dashed") +
  geom_line(data = filter(CCFs_tall, Type %in% c("False Positive")), aes(x = Feature, y = Value, colour = Type, group = id), alpha = 1, size = 0.8, linetype = "dashed") +
  geom_line(data = filter(pcp_data_tall, Type %in% c("True Positive")), aes(x = Feature, y = Value, colour = Type, group = Type), size = 2) +
  ylab("Normalized Value") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_manual(values = c("#e60000", "#000099")) +
  scale_size_manual(values = c(1, 1))

set.seed(20170222)
mysamp1 <- sample(CCFs_tall$id[CCFs_tall$Type == "True Negative"], 226)
mysamp2 <- sample(CCFs_tall$id[CCFs_tall$Type == "False Negative"], 20)
trueneg_sample <- CCFs_tall %>%
  filter(id %in% mysamp1)
falseneg_sample <- CCFs_tall %>% 
  filter(id %in% mysamp2)

p2 <- ggplot() +
  #geom_line(data = filter(CCFs_tall, Type %in% c("True Negative", "False Negative")), aes(x = Feature, y = Value, colour = Type, group = id, alpha = Type, size = Type)) +
  geom_line(data = trueneg_sample, aes(x = Feature, y = Value, colour = Type, group = id), alpha = 0.1, size = 0.2, linetype = "dashed") +
  geom_line(data = falseneg_sample, aes(x = Feature, y = Value, colour = Type, group = id), alpha = 1, size = 0.4, linetype = "dashed") +
  theme_bw() +
  geom_line(data = filter(pcp_data_tall, Type %in% c("True Negative")), aes(x = Feature, y = Value, colour = Type, group = Type), size = 2) +
  ylab("Normalized Value") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_manual(values = c("#e60000", "#000099"))

@@

## Produce plot
ggplot(result, aes(x = level, y = value, colour = fixed)) +
    facet_wrap(~metric, nrow = 2) +
    geom_point() +
    geom_line() +
    theme_bw() +
    scale_x_continuous(breaks = c(0, .125, .25, .375, .5, .625, .75), labels = c("100%", "87.5%", "75%", "62.5%", "50%", "37.5%", "25%")) +
    xlab("Land Proportion")
```

@@

ggplot(data = feature_exp, aes(x = level, y = value, colour = fixed)) +
    geom_point() +
    geom_line() +
    theme_bw() +
    theme(legend.position = "bottom") +
    scale_x_continuous(breaks = c(0, .25, .5, .75), labels = c("100%", "75%", "50%", "25%")) +
    xlab("Land Proportion") +
    facet_wrap(~feature, scales = "free_y")
```

@@

ggplot(data = feature_exp2, aes(x = level, y = value, colour = fixed)) +
    geom_point() +
    geom_line() +
    theme_bw() +
    theme(legend.position = "bottom") +
    scale_x_continuous(breaks = c(0, .25, .5, .75), labels = c("100%", "75%", "50%", "25%")) +
    xlab("Land Proportion") +
    facet_wrap(~feature, scales = "free_y")
```

@@

ggplot(data = result, aes(x = match, y = score, fill = match)) +
    geom_boxplot() +
    coord_flip() +
    scale_fill_brewer("Bullet Land Pairs", palette="Paired") +
    theme_bw() +
    theme(legend.background = element_rect(colour="grey75"),
          axis.text.y = element_blank(),
          axis.title.y = element_blank())
```

@@

>>>>

custom <- list(
  theme_bw(),
  scale_linetype_manual(values=3:2),
  scale_colour_manual(values=c("black", "grey40")),
  ylab(expression(paste("Relative Height (in ",mu,m,")", sep=""))), 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep="")))
  )

p1 <- ggplot(data = final_profs, aes(x = y, y = l30, colour = profile_id)) +
    geom_line(aes(linetype=profile_id)) +
    custom

p2 <- ggplot(data = final_doublesmoothed, aes(x = y, y = l30, colour = profile_id)) +
    geom_line(aes(linetype=profile_id)) +
    geom_smooth(inherit.aes = FALSE, aes(x = y, y = avgl30), size = .5, se=FALSE, colour="black") +
    custom

p3 <- ggplot(data = final_doublesmoothed, aes(x = y, y = l50, colour = profile_id)) +
    geom_line(aes(linetype=profile_id)) +
    geom_hline(yintercept=0, size = .5, colour="black") +
    custom +
  ylab("Adjusted relative height")

@@

```{r roughcordist, echo=FALSE, out.width='.5\\textwidth',  fig.cap='Empirical CDFs of the Roughness Correlation compared to the CCF for known matches and known non-matches. It can be seen that the distribution of each feature for the known non-matches is quite symmetric, while the distribution for each feature for the known matches is skewed left.'}
cor_compare <- CCFs_withlands %>%
  select(ccf, rough_cor, match) %>%
  gather(key = feature, value = value, ccf, rough_cor) %>%
  mutate(match = factor(match, labels = c("Known non-matches (KNM)", "Known matches (KM)")))

custom <- list(
  theme_bw(),
  scale_linetype_manual("Bullet Land Pairs", values=3:2),
  scale_colour_manual("Bullet Land Pairs", values=c("black", "grey40"))
  )

ggplot(data = cor_compare, aes(x = value, colour=match, linetype = match)) +
  stat_ecdf() +
  facet_wrap(~feature, nrow = 2) +
  ylab("") + xlab("") +
  theme(legend.background = element_rect(colour="grey75"),
        axis.title.y=element_blank(),
        plot.margin = unit(c(0,0,0,0), unit="cm")) +
  custom +
    theme(legend.position=c(0.2, 0.85)) 
```

@@

CCFs_test_normalized <- CCFs_test %>% select(Type, ccf, rough_cor, D, matches, mismatches, cms, non_cms, sum_peaks)
CCFs_test_normalized[,-1] <- lapply(CCFs_test_normalized[,-1], function(x) { (x - mean(x, na.rm = TRUE)) / sd(x, na.rm = TRUE) })
pcp_data <- CCFs_test_normalized %>%
  group_by(Type) %>%
  summarise_each(funs(mean))
pcp_data_tall <- pcp_data %>%
  gather(key = Feature, value = Value, 2:ncol(.))
CCFs_tall <- CCFs_test_normalized %>%
  mutate(id = 1:nrow(.)) %>%
  select(id, everything()) %>%
  gather(key = Feature, value = Value, 3:ncol(.)) %>%
  mutate(x = as.numeric(as.factor(Feature)))

truepos <- filter(CCFs_tall, Type %in% c("True Positive"))
falsepos <- filter(CCFs_tall, Type %in% c("False Positive"))

truepos_poly <- truepos %>% 
  group_by(Feature) %>% 
  summarize(min = min(Value), max=max(Value), mean=mean(Value), x=x[1])
tpps <- truepos_poly %>% gather(Type, Result, min:max)
tpps$order <-c(1:8, 9+8:1)
tpps$x <-c(1:8, 1:8)

tpps <- tpps %>% arrange(order)

p1 <- ggplot() +
  geom_polygon(aes(x = x, y=Result), data = tpps, fill="grey50", alpha=.35) +
  geom_line(aes(x = x, y = mean), data = truepos_poly, colour="grey50", size=1) +
  geom_line(data = truepos, aes(x = x, y = Value, colour = Type, group = id, linetype=Type), alpha = 0.1, size = 0.2) + #, linetype = "dashed") +
  scale_x_continuous(breaks=1:8, labels=unique(tpps$Feature)) +
  geom_line(data = falsepos, aes(x = x, y = Value, colour = Type, group = id, linetype=Type), alpha = 1, size = 0.8) +
  ylab("Normalized Value") +
  xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_manual(values = c("grey10", "grey50")) +
#  scale_color_manual(values = c("#e60000", "#000099")) +
  scale_size_manual(values = c(1, 1)) +
  scale_linetype_manual(values=2:1)

# p1 <- ggplot() +
# #  geom_polygon(aes(x = x, y=Result), data = tpps, fill="#000099", alpha=.5) +
#   geom_line(data = truepos, aes(x = Feature, y = Value, colour = Type, group = id), alpha = 0.1, size = 0.2, linetype = "dashed") +
#   geom_line(data = falsepos, aes(x = Feature, y = Value, colour = Type, group = id), alpha = 1, size = 0.8, linetype = "dashed") +
#   geom_line(data = filter(pcp_data_tall, Type %in% c("True Positive")), aes(x = Feature, y = Value, colour = Type, group = Type), size = 2) +
#   ylab("Normalized Value") +
#   theme_bw() +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
#   scale_color_manual(values = c("#e60000", "#000099")) +
#   scale_size_manual(values = c(1, 1))

set.seed(20170222)
mysamp1 <- sample(CCFs_tall$id[CCFs_tall$Type == "True Negative"], 226)
mysamp2 <- sample(CCFs_tall$id[CCFs_tall$Type == "False Negative"], 20)

CCFs_tall <- CCFs_tall %>% mutate(x = as.numeric(as.factor(Feature)))

trueneg_sample <- CCFs_tall %>%
  filter(id %in% mysamp1) 
falseneg_sample <- CCFs_tall %>% 
  filter(id %in% mysamp2)

trueneg_poly <- trueneg_sample %>% 
  group_by(Feature) %>% 
  summarize(min = min(Value), max=max(Value), mean=mean(Value), x=x[1])
tnps <- trueneg_poly %>% gather(Type, Result, min:max)
tnps$order <-c(1:8, 9+8:1)
tnps$x <-c(1:8, 1:8)

tnps <- tnps %>% arrange(order)

p2 <- ggplot() +
  geom_polygon(aes(x = x, y=Result), data = tnps, fill="grey50", alpha=.35) +
  geom_line(aes(x = x, y = mean), data = trueneg_poly, colour="grey50", size=1) +
  geom_line(data = trueneg_sample, aes(x = x, y = Value, colour = Type, group = id, linetype=Type), alpha = 0.1, size = 0.2) + #, linetype = "dashed") +
scale_x_continuous(breaks=1:8, labels=unique(tpps$Feature)) +
  geom_line(data = falseneg_sample, aes(x = x, y = Value, colour = Type, group = id, linetype=Type), alpha = 1, size = 0.8) +
  ylab("Normalized Value") +
  xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_manual(values = c("grey10", "grey50")) +
#  scale_color_manual(values = c("#e60000", "#000099")) +
  scale_size_manual(values = c(1, 1)) +
  scale_linetype_manual(values=2:1)

# p2 <- ggplot() +
#   #geom_line(data = filter(CCFs_tall, Type %in% c("True Negative", "False Negative")), aes(x = Feature, y = Value, colour = Type, group = id, alpha = Type, size = Type)) +
#   geom_line(data = trueneg_sample, aes(x = Feature, y = Value, colour = Type, group = id), alpha = 0.1, size = 0.2, linetype = "dashed") +
#   geom_line(data = falseneg_sample, aes(x = Feature, y = Value, colour = Type, group = id), alpha = 1, size = 0.4, linetype = "dashed") +
#   theme_bw() +
#   geom_line(data = filter(pcp_data_tall, Type %in% c("True Negative")), aes(x = Feature, y = Value, colour = Type, group = Type), size = 2) +
#   ylab("Normalized Value") +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
#   scale_color_manual(values = c("#e60000", "#000099"))

@@

## Produce plot
ggplot(result, aes(x = level, y = value, colour = fixed, linetype=fixed)) +
    facet_wrap(~metric, nrow = 2) +
    geom_point() +
    geom_line() +
    theme_bw() +
    scale_x_continuous(breaks = c(0, .125, .25, .375, .5, .625, .75), labels = c("100%", "87.5%", "75%", "62.5%", "50%", "37.5%", "25%")) +
    xlab("Land Proportion") +
  scale_colour_manual(values=c("black", "grey20", "grey30", "grey40")) +
  theme(legend.key.width=unit(3,"line"))
```

@@

ggplot(data = feature_exp, aes(x = level, y = value, colour = fixed, linetype=fixed)) +
    geom_point() +
    geom_line() +
    theme_bw() +
    theme(legend.position = "bottom") +
    scale_x_continuous(breaks = c(0, .25, .5, .75), labels = c("100%", "75%", "50%", "25%")) +
    xlab("Land Proportion") +
    facet_wrap(~feature, scales = "free_y") +
    scale_colour_manual(values=c("black", "grey20", "grey30", "grey40")) +
  theme(legend.key.width=unit(3,"line"))

```

@@

ggplot(data = feature_exp2, aes(x = level, y = value, colour = fixed, linetype=fixed)) +
    geom_point() +
    geom_line() +
    theme_bw() +
    theme(legend.position = "bottom") +
    scale_x_continuous(breaks = c(0, .25, .5, .75), labels = c("100%", "75%", "50%", "25%")) +
    xlab("Land Proportion") +
    facet_wrap(~feature, scales = "free_y") +
    scale_colour_manual(values=c("black", "grey20", "grey30", "grey40")) +
  theme(legend.key.width=unit(3,"line"))

```

@@

ggplot(data = result, aes(x = match, y = score, fill = match)) +
    geom_boxplot() +
    coord_flip() +
    scale_fill_brewer("Bullet Land Pairs", palette="Paired") +
    theme_bw() +
    theme(legend.position="none",
          axis.text.y = element_blank(),
          axis.title.y = element_blank()) +
  annotate("text", x=2.25, y= 0.8, label="Known matches (KM)", hjust=1, colour="grey40") +
  annotate("text", x=0.75, y= 0.05, label="Known non-matches (KNM)", hjust=0, colour="grey40")

```

@@

# Acknowledgment

We wish to acknowledge the anonymous reviewers, whose quick yet thorough and immensely helpful reviews helped us improve this manuscript. We greatly appreciate the extra effort put forth for us.
